---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  echo = FALSE
)
```

# The Coursera R Capstone Project

The Coursera R Capstone Project examines earthquack data from
Imports the U.S. National Oceanographic and Atmospheric Administation's (NOAA) 
dataset of significant earthquakes for more info, visit: 
\hret{https://www.ngdc.noaa.gov/nndc/struts/form?t=101650&s=1&d=1}{click here}

## Installation

You can install RCapstone from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("arthurgailes/RCapstone")
```

## Load cleaned data

This loads the earthquake data used for the graphs

```{r load_data, eval=FALSE}
data <- eq_clean_data()
```

## Earthquakes in US and China after 2000

This graphs earthquakes in US and China after 2000; the radius of the circles charts the richter-scale magnitude of the earthquakes.

```{r graph_timeline, eval=T}
geom_timeline()
```

## Labeled arthquakes in US and China after 2000

This graphs earthquakes in US and China after 2000; the radius of the circles
charts the richter-scale magnitude of the earthquakes. The largest earthquakes are labeled.

```{r graph_timeline_labeled, eval=T}
geom_timeline_label()
```

## Map of earthquakes in Mexico

Generates a Map of earthquakes in Mexico after 2000. The radius of the circles corresponds to the magnitude of the earthquakes.

```{r Mexico_map, eval=T}
eq_map()
```