---
title: "R Capstone Model Details"
author: "Arthur Gailes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This project displays the data cleaning, visualization, and R package programming skills learned in the Coursera/Johns Hopkins Mastering Software Development in R course.

The data examined is the U.S. National Oceanographic and Atmospheric Administation's (NOAA)  dataset of significant earthquakes. For more info, visit: [click here](https://www.ngdc.noaa.gov/nndc/struts/form?t=101650&s=1&d=1).

## Installation

You can install RCapstone from github with:

```{r gh-installation, eval = T}
# install.packages("devtools")
devtools::install_github("arthurgailes/RCapstone")
```

## Reading and cleaning data.

The functions *eq_clean_data* and *eq_location_data* format the NOAA dataset to return data on earthquake details and location, respectively. Both functions are used to produce the graphs in the data. 
```{r load_data, eval=T}
data <- eq_clean_data()
cities <- eq_location_clean()
```

## Earthquakes in US and China after 2000

This graphs earthquakes in US and China after 2000; the radius of the circles charts the richter-scale magnitude of the earthquakes.

```{r graph_timeline, eval=F}
geom_timeline()
```

## Labeled arthquakes in US and China after 2000

This graphs earthquakes in US and China after 2000; the radius of the circles
charts the richter-scale magnitude of the earthquakes. The largest earthquakes are labeled.

```{r graph_timeline_labeled, eval=F}
geom_timeline_label()
```

## Map of earthquakes in Mexico

Generates a Map of earthquakes in Mexico after 2000. The radius of the circles corresponds to the magnitude of the earthquakes.

```{r Mexico_map, eval=F}
eq_map()
```